---
title: "Metacritic Scraping"
output: html_notebook
---

```{r}
library(tidyverse)
library(rvest)
library(lubridate)
library(tidytext)
library(plotly)
```

```{r}
# Reading in pages and extracting hyperlinks
result <- vector("list",10)

for(i in 0:9) {
  webpage <- read_html(paste0("https://www.metacritic.com/browse/games/release-date/available/ps4/metascore?page=", i))
  loop_links <- webpage %>% html_nodes("#main .product_title a") %>% html_attr('href')
  loop_links_proper <- paste0("https://www.metacritic.com", loop_links)
  result[[i+1]] <- loop_links_proper
}

# Joining results into a single vector
all_links <- unlist(result)
```

```{r}
#game_page <- read_html("https://www.metacritic.com/game/playstation-4/wolfenstein-ii-the-new-colossus")
```

```{r}
# Getting all the attributes

final_result <- vector("list", 1812)
names(final_result) <- all_links

for(i in all_links) {
#game_page <- read_html("https://www.metacritic.com/game/playstation-4/wolfenstein-ii-the-new-colossus")
game_page <- read_html(i)

title <- game_page %>% html_nodes("h1") %>% html_text()
release_date <- game_page %>% html_nodes(".release_data .data") %>% html_text()
developer <- game_page %>% html_nodes(".developer .data") %>% html_text()
publisher <- game_page %>% html_nodes(".publisher a") %>% html_text()
genre <- game_page %>% html_nodes(".product_genre .data") %>% html_text()
score <- game_page %>% html_nodes(".positive span, .mixed span, .negative span") %>% html_text()
review_count <- game_page %>% html_nodes(".highlight_metascore .count a") %>% html_text()
description <- game_page %>% html_nodes(".data .blurb_expanded") %>% html_text()

title <- ifelse(length(title) == 0, "Notapplicable", title)
release_date <- ifelse(length(release_date) == 0, "Notapplicable", release_date)
developer <- ifelse(length(developer) == 0, "Notapplicable", developer)
publisher <- ifelse(length(publisher) == 0, "Notapplicable", publisher)
genre <- ifelse(length(genre) == 0, "Notapplicable", genre)
score <- ifelse(length(score) == 0, "Notapplicable", score)
review_count <- ifelse(length(review_count) == 0, "Notapplicable", review_count)
description <- ifelse(length(description) == 0, "Notapplicable", description)

genre <- paste(genre, collapse = ', ')

# Creating table entry from vectors
final_result[[i]] <- data.frame(title, release_date, developer, publisher, genre, score, review_count, description)

print(score)

}
```

```{r}
temp_results <- final_result
```


The loop got stopped at the 14th iteration. This means the scraping process is really fast as it only took around 30s to scrape 14 games.

I got a bit stuck. I'm creating this data frame with each iteration, but when I get an empty value, I can't assemble my data frame. I need a way to check if my vector is empty, and if it is, need to put an "NA" as the value.

I really need to invest in a progress bar for my loops. I have no way of knowing how far along I am. Since my indices are character vectors, I would need to name them as indices and refer to the position in my vector from my index. I'm gonna implement progress bars next time because this is a pain in the ass.

This is an OK way to track progress, it prints the score so I can track how far along it is. I will use progress bars next time.

Another thing to consider is skipping iterations if the for loop fails. In this case, I got a 404 error opening a site. Need to skip these errors.

Let's carry on with the temp result.
 

```{r}
dataset <- do.call("rbind", temp_results)
```

The script is not perfect as it truncates the genre to a single value, something to look out for. Also, the description is taken as a single scraped category, which leaves a lot of values empty. I'm fairly happy with this overall. Time to clean up the data.

696 of the 1607 games have missing descriptions, which is 43%. Not ideal but workable

```{r}
dataset$title <- as.character(dataset$title)
dataset$release_date <- as.character(dataset$release_date)
dataset$release_date <- mdy(dataset$release_date)
dataset$developer <- as.character(dataset$developer)
dataset$publisher <- as.character(dataset$publisher)
dataset$genre <- as.character(dataset$genre)
dataset$score <- as.numeric(as.character(dataset$score))
dataset$review_count <- as.character(dataset$review_count)
dataset$review_count <- gsub(" Critics", "", dataset$review_count)
dataset$review_count <- as.numeric(dataset$review_count)
dataset$description <- as.character(dataset$description)
```

Alright, the dataset is pretty tidy with variables in the right format. I'm quite happy with this.

Further work would try to find games/movies that are divisive in terms of ratings. For this, not only do I have to scrape all games and their respective information, but go into their reviews page and scrape all of the scores. This is relatively straightforward bacause I can append "/critic-reviews" to each URL and get a list of all scores as well as the corresponding title. 

You can scrape: "h1 , #main .indiv"